Vagueness \& Rationality

### 2018-08-25 springer/current/e1.tex
recompiling

\begin{table}
\centering
\caption{Experiment 1 instructions arranged by condition. The instructions given in the table started with ``Choose \ldots"}
\label{instructionsC-exp-1}
\begin{tabular}{cccll}
\hline\noalign{\smallskip}
Item & Quantity & Number & Crisp & Vague\\
\noalign{\smallskip}\hline\noalign{\smallskip}
06:15:24 & Small & Numeric & the square with 6 dots & a square with about 10 dots\\
06:15:24 & Small & Verbal & the square with the fewest dots & a square with few dots\\
06:15:24 & Large & Numeric & the square with 24 dots & a square with about 20 dots\\
06:15:24 & Large & Verbal & the square with the most dots & a square with many dots\\
\noalign{\smallskip}\hline\noalign{\smallskip}
16:25:34 & Small & Numeric & the square with 16 dots & a square with about 20 dots\\
16:25:34 & Small & Verbal & the square with the fewest dots & a square with few dots\\
16:25:34 & Large & Numeric & the square with 34 dots & a square with about 30 dots\\
16:25:34 & Large & Verbal & the square with the most dots & a square with many dots\\
\noalign{\smallskip}\hline\noalign{\smallskip}
26:35:44 & Small & Numeric & the square with 26 dots & a square with about 30 dots\\
26:35:44 & Small & Verbal & the square with the fewest dots & a square with few dots\\
26:35:44 & Large & Numeric & the square with 44 dots & a square with about 40 dots\\
26:35:44 & Large & Verbal & the square with the most dots & a square with many dots\\
\noalign{\smallskip}\hline\noalign{\smallskip}
36:45:54 & Small & Numeric & the square with 36 dots & a square with about 40 dots\\
36:45:54 & Small & Verbal & the square with the fewest dots & a square with few dots\\
36:45:54 & Large & Numeric & the square with 54 dots & a square with about 50 dots\\
36:45:54 & Large & Verbal & the square with the most dots & a square with many dots\\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

@@

\subsection{Hypotheses}

@@

\begin{description}
	\item [Hypothesis 1] There exists a main effect RT advantage for vagueness.
	\item [Hypothesis 2] An RT advantage for vagueness both in \emph{numeric} and in \emph{verbal} instructions.
	\item [Hypothesis 3] No large main effect of instruction format (i.e., numeric versus verbal) since we hypothesised that vagueness rather than instruction format drove the effect in Experiment 1.
	\item [Hypothesis 4] On the basis of Experiment 1, we expect faster responses for stimuli with more discriminable arrays.(i.e., an effect of item).
	\item [Hypothesis 5] Participants should make more borderline case choices for vague than crisp instructions.
\end{description}

\subsection{Experimental Method}

@@

\subsection{Results}

@@

\begin{description}
	\item [Test of Hypothesis 1] The main effect of \emph{vagueness} was to slow responses down, in contrast with Experiment 1, and offering evidence against Hypothesis 1 (vague: 2668 ms; crisp: 2450 ms; a difference of 218 ms; $\beta=.06$, $se=.01$, $t=4.6$, $p<0.0001$). 
	\item [Test of Hypothesis 2] In focussed comparisons, vagueness was significantly disadvantageous in the \emph{numeric} conditions ($\beta=0.09$, $se=0.02$, $t=4.5$, $p<0.0001$), and non-significantly disadvantageous in the \emph{verbal} conditions ($\beta=0.02$, $se=0.02$, $t=1.5$, $p=0.1550$), offering partial evidence against Hypothesis 2. The disadvantage for vagueness was greater in the numerical than in the verbal conditions, leading to a significant overall interaction effect between vagueness and instruction format ($\beta=-0.13$, $se=0.02$, $t=-6.6$, $p=0.0169$).
	\item [Test of Hypothesis 3] There was a significant effect of \emph{instruction format} with numerical conditions attracting longer responses than the verbal conditions: consistent with Experiment 1, but suggesting that instruction format rather than vagueness drove the effect we observed in Experiment 1 (numeric: 3284 ms; verbal 1866 ms; a difference of 1418 ms; ($\beta=-0.36$, $se=0.07$, $t=-5.1$, $p<0.0001$).
	\item [Test of Hypothesis 4] There was a significant main effect of item (i.e., of which triple of numbers of dots were used in the stimulus): ($\beta=0.12$, $se=0.02$, $t=7.1$, $p<0.0001$). This effect seems likely to be due to the very fast responses for stimuli using arrangements of the smallest numbers of dots (6,15,24), which also had the largest difference in ratio of smallest number to largest number in the stimulus, suggesting that stimuli using these numbers of dots may have been particularly discriminable for participants.
\end{description}

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim = 20mm 0mm 35mm 0mm, clip, width=.49\textwidth]{figures/Ce1-rtplot-1.pdf}
\includegraphics[trim = 20mm 0mm 35mm 0mm, clip, width=.49\textwidth]{figures/Ce1-blBarChart-1}
\caption{Experiment 1 results: mean response times by condition and item, and counts of borderline case responses by condition.}
\label{resultsC-exp-1}
\end{figure}

\subsection{Discussion}

Experiment 1 tested to see whether when borderline cases are present, vague instructions would speed responses as they did in Experiment pilot exp 2 when there were no borderline squares.

We actually found a small (but statistically significant) \emph{disadvantage} of vague instructions: vague instructions slowed people down by 112 ms on average. We also found that the effect of instruction format was significant, with numerical format slowing responses by 689 ms on average, such that the disadvantage of numerical format overwhelmed the contribution of vagueness. The \emph{verbal vague} condition was still responded to faster than the \emph{numerical crisp} condition, so the pattern from Experiment pilot exp 2 was reproduced, but in the light of the evidence from Experiment 1, in the presence of borderline cases, the advantage that was ascribed to vagueness before now looks more like an advantage of verbal instruction format.

>>>>

\begin{table}[htbp]
\centering
\caption{Experiment 1 instructions arranged by condition. The instructions given in the table started with ``Choose \ldots"}
\label{instructionsC-exp-1}
\begin{tabular}{cccll}
\hline\noalign{\smallskip}
Item & Quantity & Number & Crisp & Vague\\
\noalign{\smallskip}\hline\noalign{\smallskip}
06:15:24 & Small & Numeric & the square with 6 dots & a square with about 10 dots\\
06:15:24 & Small & Verbal & the square with the fewest dots & a square with few dots\\
06:15:24 & Large & Numeric & the square with 24 dots & a square with about 20 dots\\
06:15:24 & Large & Verbal & the square with the most dots & a square with many dots\\
\noalign{\smallskip}\hline\noalign{\smallskip}
16:25:34 & Small & Numeric & the square with 16 dots & a square with about 20 dots\\
16:25:34 & Small & Verbal & the square with the fewest dots & a square with few dots\\
16:25:34 & Large & Numeric & the square with 34 dots & a square with about 30 dots\\
16:25:34 & Large & Verbal & the square with the most dots & a square with many dots\\
\noalign{\smallskip}\hline\noalign{\smallskip}
26:35:44 & Small & Numeric & the square with 26 dots & a square with about 30 dots\\
26:35:44 & Small & Verbal & the square with the fewest dots & a square with few dots\\
26:35:44 & Large & Numeric & the square with 44 dots & a square with about 40 dots\\
26:35:44 & Large & Verbal & the square with the most dots & a square with many dots\\
\noalign{\smallskip}\hline\noalign{\smallskip}
36:45:54 & Small & Numeric & the square with 36 dots & a square with about 40 dots\\
36:45:54 & Small & Verbal & the square with the fewest dots & a square with few dots\\
36:45:54 & Large & Numeric & the square with 54 dots & a square with about 50 dots\\
36:45:54 & Large & Verbal & the square with the most dots & a square with many dots\\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

@@

\subsection{Hypotheses (Experiment 1)}

@@

\begin{description}
	\item [Hypothesis 1] There exists a main effect RT advantage for vagueness.
	\item [Hypothesis 2] An RT advantage for vagueness both in \emph{numeric} and in \emph{verbal} instructions.
	\item [Hypothesis 3] No large main effect of instruction format (i.e., numeric versus verbal) since we hypothesised that vagueness rather than instruction format drove the effect in Experiment 1.
	\item [Hypothesis 4] On the basis of our experiment in \citet{green2013utility}, we expect faster responses for stimuli with more discriminable arrays.(i.e., an effect of item).
	\item [Hypothesis 5] Participants should make more borderline case choices for vague than crisp instructions.
\end{description}

\subsection{Experimental Method (Experiment 1)}

@@

\subsection{Results (Experiment 1)}

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim = 20mm 0mm 30mm 0mm, clip, width=.49\textwidth]{figures/Ce1-rtplot-1.pdf}
\includegraphics[trim = 20mm 0mm 25mm 0mm, clip, width=.49\textwidth]{figures/Ce1-blBarChart-1}
\caption{Experiment 1 results: mean response times by condition and item, and counts of borderline case responses by condition.}
\label{resultsC-exp-1}
\end{figure}

\begin{description}
	\item [Test of Hypothesis 1] The main effect of \emph{vagueness} was to slow responses down, in contrast with Experiment 1, and offering evidence against Hypothesis 1 (vague: 2668 ms; crisp: 2450 ms; a difference of 218 ms; $\beta=.06$, $se=.01$, $t=4.6$, $p<0.0001$). 
	\item [Test of Hypothesis 2] In focussed comparisons, vagueness was significantly disadvantageous in the \emph{numeric} conditions ($\beta=0.09$, $se=0.02$, $t=4.5$, $p<0.0001$), and non-significantly disadvantageous in the \emph{verbal} conditions ($\beta=0.02$, $se=0.02$, $t=1.5$, $p=0.1550$), offering partial evidence against Hypothesis 2. The disadvantage for vagueness was greater in the numerical than in the verbal conditions, leading to a significant overall interaction effect between vagueness and instruction format ($\beta=-0.13$, $se=0.02$, $t=-6.6$, $p=0.0169$).
	\item [Test of Hypothesis 3] There was a significant effect of \emph{instruction format} with numerical conditions attracting longer responses than the verbal conditions: consistent with Experiment 1, but suggesting that instruction format rather than vagueness drove the effect we observed in \citet{green2013utility} (numeric: 3284 ms; verbal 1866 ms; a difference of 1418 ms; ($\beta=-0.36$, $se=0.07$, $t=-5.1$, $p<0.0001$).
	\item [Test of Hypothesis 4] There was a significant main effect of item (i.e., of which triple of numbers of dots were used in the stimulus): ($\beta=0.12$, $se=0.02$, $t=7.1$, $p<0.0001$). This effect seems likely to be due to the very fast responses for stimuli using arrangements of the smallest numbers of dots (6,15,24), which also had the largest difference in ratio of smallest number to largest number in the stimulus, suggesting that stimuli using these numbers of dots may have been particularly discriminable for participants.
\end{description}

@@

\subsection{Discussion (Experiment 1)}

Experiment 1 tested to see whether when borderline cases are present, vague instructions would speed responses as they did in our experiment in \citet{green2013utility} when there were no borderline squares.

We actually found a small (but statistically significant) \emph{disadvantage} of vague instructions: vague instructions slowed people down by 112 ms on average. We also found that the effect of instruction format was significant, with numerical format slowing responses by 689 ms on average, such that the disadvantage of numerical format overwhelmed the contribution of vagueness. The \emph{verbal vague} condition was still responded to faster than the \emph{numerical crisp} condition, so the pattern from \citet{green2013utility} was reproduced, but in the light of the evidence from Experiment 1, in the presence of borderline cases, the advantage that was ascribed to vagueness before now looks more like an advantage of verbal instruction format.

### 2018-08-25 springer/current/e2.tex
recompiling

\subsection{Hypotheses}

For Experiment 2, we hypothesised:

\begin{description}
	\item [Hypothesis 1] Vague instructions are easier for the reader than crisp ones (main effect of vagueness)
	\item [Hypothesis 2] Comparison is easier for the reader than matching (main effect of selection task)
	\item [Hypothesis 3] Effects of vagueness are different depending on whether the selection task is matching or comparison (interaction effect selection x vagueness).
\end{description}

\subsection{Experimental Method}

@@

\subsection{Results}

We used the method proposed by \citet{Levy:MainEffectsInteractions} to test for the main effect of Vagueness in the presence of its higher-order interactions.

@@

\begin{description}
	\item [Test of Hypothesis 1] Vague instructions were non-significantly easier for the reader than crisp instructions when vagueness was considered as a main effect ($\beta=-0.01$, $se=0.01$, $t=-0.4$, $p=0.7158$). 
	\item [Test of Hypothesis 2] There was a statistically significant main effect of selection task, with the comparison task speeding responses compared to the matching task ($\beta=0.16$, $se=0.03$, $t=6.2$, $p<0.0001$). 
	\item [Test of Hypothesis 3] Vagueness exerted effects in different directions for the comparison task and for the matching task: there was a significant interaction between vagueness and selection task ($\beta=0.13$, $se=0.03$, $t=4.2$, $p<0.0001$). 
Separate analyses were conducted testing for effects of vagueness at each level of the selection task.
Within the comparison task vagueness significantly speeded response times compared with crisp controls ($\beta=-0.07$, $se=0.02$, $t=-3.5$, $p<0.0012$). 
Within the matching task vagueness significantly \emph{slowed} response times compared with crisp controls ($\beta=0.06$, $se=0.02$, $t=2.9$, $p<0.0061$). 
\end{description}

In other words, the cost reduction account was wrong to predict significant main effect advantages for vagueness (although there was a non-significant trend in the \emph{direction} predicted by the cost reduction account), and wrong to predict that vagueness should be beneficial at each level of the selection task: however vagueness was significantly advantageous in the comparison task.

>>>>

\subsection{Hypotheses (Experiment 2)}

For Experiment 2, we formulated the following hypotheses:

\begin{description}
\item [Hypothesis 1] Vague instructions should result in faster responses than crisp instructions (main effect of vagueness).
\item [Hypothesis 2] Instructions that allow comparison should result in faster responses than instructions that necessitate matching (main effect of selection task).
\item [Hypothesis 3] Vagueness effect should differ between comparison and matching: The effects of vagueness should differ when the selection task is comparison versus when it is matching (interaction effect selection x vagueness).
\end{description}

\subsection{Experimental Method (Experiment 2)}

@@

\subsection{Results (Experiment 2)}

%We used the method proposed by \citet{Levy:MainEffectsInteractions} to test for the main effect of Vagueness in the presence of its higher-order interactions.

@@

\begin{description} %
	\item [Test of Hypothesis 1] Vague instructions resulted in faster responses than crisp instructions on average. However this difference was not significant in the full model ($\beta=-0.0057$, $se=0.0137$, $t=-0.42$, $p=0.678$). Using Levy's method \citep{Levy:MainEffectsInteractions} to test for main effects in the presence of higher-order interactions, by doing model comparison between a null model that included all interaction terms involving Vagueness but leaving out a term for the main effect of Vagueness, against a full model that differed only by including Vagueness as a main effect, showed that the full model was no better than the reduced model (df=1, p=0.6764) - consituting more evidence that Vagueness did not exert a significant main effect on response times. 
	\item [Test of Hypothesis 2] comparison instructions resulted in faster responses than matching instructions, and the difference was significant ($\beta=0.1618$, $se=0.0255$, $t=6.34$, $p<0.001$).
	\item [Test of Hypothesis 3] Although Vagueness did not exert a significant main effect, Vagueness did exert effects in interactions with some other variables: the interaction between Vagueness and Selection task  was significant ($\beta=0.1306$, $se=0.0205$, $t=6.38$, $p<0.001$), suggesting that Vagueness speeded RTs in the comparison condition but slowed them down in the matching task. 
	Separate analyses at each level of selection \ldots
	%provided evidence that vague instructions resulted in faster responses than crisp instructions for the comparison condition (p<0.01); and slower responses than crisp instructions in the matching condition (p<0.01). 
%
%Separate analyses were conducted testing for effects of vagueness at each level of the selection task.
%Within the comparison task vagueness significantly speeded response times compared with crisp controls ($\beta=-0.07$, $se=0.02$, $t=-3.5$, $p<0.0012$). 
%Within the matching task vagueness significantly \emph{slowed} response times compared with crisp controls ($\beta=0.06$, $se=0.02$, $t=2.9$, $p<0.0061$). 
\end{description}

\subsection{Discussion (Experiment 2)}
The cost reduction account predicted that there should be a significant main effect of Vagueness such that responses would be faster for Vague intructions than for crisp instructions. We found that although there was a very small effect in that direction, the effect was not statistically significant. Models that differed only in the presence of Vagueness as a main effect were shown not to differ signigicantly in their explanatory value. However we did find that Vagueness exerted effects on other variables: Vgueness speeded RTs in the comparison task and slowed RTs in the matching task.

%In other words, the cost reduction account was wrong to predict significant main effect advantages for vagueness (although there was a non-significant trend in the \emph{direction} predicted by the cost reduction account), and wrong to predict that vagueness should be beneficial at each level of the selection task: however vagueness was significantly advantageous in the comparison task.

### 2018-08-25 springer/current/e3.tex
recompiling

\begin{figure}[htbp]
\centering
\includegraphics[width=.75\textwidth]{figures/Ee3-flow.jpg}
\caption{Experiment 3 example stimulus}
\label{Experiment3examplestimulus}
\end{figure}

@@

\subsection{Hypotheses}

@@

\subsection{Results}
40 volunteers participated. The results showed that vagueness was beneficial for comparison but detrimental for matching (the same as Experiment 2) even when no numbers were allowed in the instructions. Figure \ref{resultsE-exp-3} shows the means by condition. Our findings were as follows:

\begin{description}
	\item [Test of hypothesis 1] There was no significant main effect of vagueness ($\beta=-0.02$, $se=0.01$, $t=-1.5$, $p=0.1296$). 
	\item [Test of hypothesis 2] There was a main effect of selection, with comparison task instructions leading to faster responses than the matching task instructions ($\beta=0.18$, $se=0.02$, $t=10.4$, $p<0.0001$).  This effect was in the same direction as Experiment 3. 
	\item [Test of hypothesis 3] Vagueness did exert different effects depending on the selection task (main interaction effect of vagueness by selection $\beta=0.12$, $se=0.02$, $t=5.1$, $p<0.0001$). 
Separate analyses of the effect of vagueness were conducted for the comparison task and for the matching task using Bonferroni-adjusted significance thresholds. 
In the comparison task, vagueness resulted in faster response times ($\beta=-0.08$, $se=0.02$, $t=-4.3$, $p<0.0001$). 
In the matching task vagueness slowed response times ($\beta=0.05$, $se=0.01$, $t=3.7$, $p=0.0004$). 
These results are in the same direction as Experiment 3.
\end{description}

Once again, the cost reduction account was wrong to predict main effect advantages for vagueness, and wrong to predict that vagueness should be beneficial at each level of the selection task: however vagueness was advantageous in the comparison task.

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{figures/Ee3-rtplot-1.pdf}
\caption{Mean response times by condition for Experiment 3}
\label{resultsE-exp-3}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[width=.5\textwidth]{figures/Ee3-flow.jpg}
\caption{Experiment 3 example stimulus}
\label{Experiment3examplestimulus}
\end{figure}

@@

\subsection{Hypotheses (Experiment 3)}

@@

\subsection{Results (Experiment 3)}
40 volunteers participated. The results showed that vagueness was beneficial for comparison but detrimental for matching (the same as Experiment 2) even when no numbers were allowed in the instructions. Figure \ref{resultsE-exp-3} shows the means by condition. Our findings were as follows:

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{figures/Ee3-rtplot-1.pdf}
\caption{Mean response times by condition for Experiment 3 where all instructions were verbal}
\label{resultsE-exp-3}
\end{figure}

\begin{description}
	\item [Test of hypothesis 1] Vague instructions resulted in faster responses than crisp instructions on average. However this difference was not significant in the full model ($\beta=-0.015$, $se=0.0097$, $t=-1.58$, $p=0.119$). Using Levy's method \citep{Levy:MainEffectsInteractions} to test for main effects in the presence of higher-order interactions, by doing model comparison between a null model that included all interaction terms involving Vagueness but leaving out a term for the main effect of Vagueness, against a full model that differed only by including Vagueness as a main effect, showed that the full model was no better than the reduced model (df=1, p=0.118) - consituting more evidence that Vagueness did not exert a significant main effect on response times. 
	\item [Test of hypothesis 2] comparison instructions resulted in faster responses than matching instructions, and the difference was significant ($\beta=0.176$, $se=0.0168$, $t=10.51$, $p<0.001$).
	\item [Test of hypothesis 3] Although Vagueness did not exert a significant main effect, Vagueness did exert effects in interactions with some other variables: the interaction between Vagueness and Selection task  was significant ($\beta=0.123$, $se=0.0166$, $t=7.42$, $p<0.001$), suggesting that Vagueness speeded RTs in the comparison condition but slowed them down in the matching task. 
	Separate analyses at each level of selection \ldots
	%provided evidence that vague instructions resulted in faster responses than crisp instructions for the comparison condition (p<0.01); and slower responses than crisp instructions in the matching condition (p<0.01). 
	%
%Separate analyses of the effect of vagueness were conducted for the comparison task and for the matching task using Bonferroni-adjusted significance thresholds. 
%In the comparison task, vagueness resulted in faster response times ($\beta=-0.08$, $se=0.02$, $t=-4.3$, $p<0.0001$). 
%In the matching task vagueness slowed response times ($\beta=0.05$, $se=0.01$, $t=3.7$, $p=0.0004$). 
%These results are in the same direction as Experiment 2.
\end{description}

\subsection{Discussion (Experiment 3)}
Once again, the cost reduction account was wrong to predict main effect advantages for vagueness, and wrong to predict that vagueness should be beneficial at each level of the selection task: however vagueness was advantageous in the comparison task.

### 2018-08-25 springer/current/general-discussion.tex
finished renumbering
recompiling

To explain why this is, let us summarise our findings so far: Experiment 1 showed that responses were faster and more accurate when the instructions were vague than when they were crisp, but the experiment was unable to distinguish effects of vagueness from those of number-avoidance or selection task: the vague conditions were also in verbal rather than numerical format, and they mandated a comparison strategy rather than a matching strategy. Experiment 2 showed that number avoidance in the verbal format instructions is an important factor driving the faster response times in the task, and that vagueness does not have any additional benefit in either the verbal format instructions or the numerical format instructions. However, Experiment 2 did not distinguish benefits of number avoidance from benefits of the comparison selection task. In Experiments 3 and 4 we manipulated vagueness and the selection task, separately at each level of numerical format. Across the two experiments, we found that the comparison-task instructions attracted faster response times than the matching-task instructions. Within the two experiments we found that vagueness exerts benefits when the selection task is \emph{comparison}, but not when the task is \emph{matching}.

@@

\begin{table}[htbp]
\caption{Vagueness as range reduction: a summary of Experiments 3 and 4}
\label{Vagueness as range reduction}
\centering
\begin{tabular}{cccc}
\hline\noalign{\smallskip}
selection task 					& vagueness		& candidates	& effect of vagueness						\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\multirow{ 2}{*}{comparison} 	& crisp 		& 2				& \multirow{ 2}{*}{vagueness advantage}  	\\
\cline{2-3}
								& vague			& 1				&                                           \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\multirow{ 2}{*}{matching} 		& crisp 		& 1 			& \multirow{ 2}{*}{vagueness disadvantage}	\\
\cline{2-3}
								& vague			& 2				&								 			\\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

To see why, consider Figures 3 and 4. Both figures depict four conditions, depending on whether the expression was crisp or vague, and depending on whether the referent could be identified using a comparison strategy or not. Two of the resulting four conditions result in an expression that can denote either of two referents; the other two conditions result in an expression that can only denote one referent, with the other possible referent being a marginal candidate at best.

@@

First, the experiments by \citeauthor{Mishra01042011} suggest that it is important how much information is conveyed by an expression, and their findings are echoed by our own thoughts about range reduction (following Experiments 3 and 4). In the case of (a)--(d) above, it appears that (a) conveys the most detailed information (designating the smallest segment of the temperature scale), followed by (b), then (d), then (c) (e.g., 40 degrees is above 25, but at 40 Celsius the word ``warm'' is likely to give way to ``hot'' or ``scorching''): 
%
\begin{quote}
$a < b < d < c$
\end{quote}
%
If these hunches are correct, then it seems to us that it is relatively unimportant whether a given expression is vague or crisp. Other factors seem more important; moreover, it may depend on the task and the audience which of a-d is preferred. For example, an \emph{expert} may prefer to read expression (a), because it gives her the most detailed information on which to base her decisions. On the other hand, expression (d) (``warm'') is shorter than the other three and avoids the use of numbers; our experiments suggest that this may make (d) more rapidly understood than its competitors; earlier experiments point in the same direction, given the evaluative nature of ``warm'' (see our section 1 and  \citeauthor{peters2009bringing}), which is especially important if the hearer is unfamiliar with the metric used. These considerations suggest that {\em non-experts} might prefer expression (d).

>>>>

To explain why this is, let us summarise our findings so far: %
%\citet{green2013utility} showed that responses were faster and more accurate when the instructions were vague than when they were crisp, but the experiment was unable to distinguish effects of vagueness from those of number-avoidance or selection task: the vague conditions were also in verbal rather than numerical format, and they mandated a comparison strategy rather than a matching strategy. 
%
Experiment 1 showed that number avoidance in the verbal format instructions is an important factor driving the faster response times in the task, and that vagueness does not have any additional benefit in either the verbal format instructions or the numerical format instructions. However, Experiment 1 did not distinguish benefits of number avoidance from benefits of the comparison selection task. In Experiments 2 and 3 we manipulated vagueness and the selection task, separately at each level of numerical format. Across the two experiments, we found that the comparison-task instructions attracted faster response times than the matching-task instructions. Within the two experiments we found that vagueness exerts benefits when the selection task is \emph{comparison}, but not when the task is \emph{matching}.

@@

\begin{table}[htbp]
\caption{Vagueness as range reduction: a summary of Experiments 2 and 3}
\label{Vagueness as range reduction}
\centering
\begin{tabular}{cccc}
\hline\noalign{\smallskip}
selection task 					& vagueness		& candidates	& effect of vagueness						\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\multirow{ 2}{*}{comparison} 	& crisp 		& 2				& \multirow{ 2}{*}{vagueness advantage}  	\\
\noalign{\smallskip}\cline{2-3}\noalign{\smallskip}
								& vague			& 1				&                                           \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\multirow{ 2}{*}{matching} 		& crisp 		& 1 			& \multirow{ 2}{*}{vagueness disadvantage}	\\
\noalign{\smallskip}\cline{2-3}\noalign{\smallskip}
								& vague			& 2				&								 			\\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

To see why, consider Figures \ref{resultsD-exp-2} and \ref{resultsE-exp-3}. Both figures depict four conditions, depending on whether the expression was crisp or vague, and depending on whether the referent could be identified using a comparison strategy or not. Two of the resulting four conditions result in an expression that can denote either of two referents; the other two conditions result in an expression that can only denote one referent, with the other possible referent being a marginal candidate at best.

@@

First, the experiments by \citeauthor{Mishra01042011} suggest that it is important how much information is conveyed by an expression, and their findings are echoed by our own thoughts about range reduction (following Experiments 2 and 3). In the case of (a)--(d) above, it appears that (a) conveys the most detailed information (designating the smallest segment of the temperature scale), followed by (b), then (d), then (c) (e.g., 40 degrees is above 25, but at 40 Celsius the word ``warm'' is likely to give way to ``hot'' or ``scorching''): 
%
\begin{quote}
$a < b < d < c$
\end{quote}
%
If these hunches are correct, then it seems to us that it is relatively unimportant whether a given expression is vague or crisp. Other factors seem more important; moreover, it may depend on the task and the audience which of a-d is preferred. For example, an \emph{expert} may prefer to read expression (a), because it gives her the most detailed information on which to base her decisions. On the other hand, expression (d) (``warm'') is shorter than the other three and avoids the use of numbers; our experiments suggest that this may make (d) more rapidly understood than its competitors; earlier experiments point in the same direction, given the evaluative nature of ``warm'' (see our section 1 and  \citeauthor{peters2009bringing}), which is especially important if the hearer is unfamiliar with the metric used. These considerations suggest that {\em non-experts} might prefer expression (d).
